Meta-analysis

### 2019-11-12 04_Prep_data.Rmd
Added trial variance

>>>>

```{r Trial_variance}

slimmer_PM_dat$SSquare <- 
   slimmer_PM_dat$yield_error * (slimmer_PM_dat$n - 1)

slimmer_PM_dat$pop_var <- NA

for(i in unique(slimmer_PM_dat$trial)){
   pop_var <- sqrt(
      sum(slimmer_PM_dat[slimmer_PM_dat$trial == i,"SSquare"])/
         sum(slimmer_PM_dat[slimmer_PM_dat$trial == i,"n"])
      )

slimmer_PM_dat[slimmer_PM_dat$trial == i, "pop_var"] <- pop_var

write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
